---
title       : MPG Prediction
subtitle    : Data Product project
author      : Vasily Vinogradov
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Shine App Information

This application is built to demonstrate shiny app functionality. It is basically linear regression project. 

---
## Data Source

Source data is standard mtcars data set. 

```{r}
head(mtcars,10)
```

---
## Model description

We build a linear regression model to predict miles per gallon (mpg) with 3 variables :

* Q Sec
* Car weight
* Transmission type

```{r eval=FALSE}
fit3 <- lm(mpg ~ wt + am + qsec, data=mtcars)  
```

---
## Input and output

You can change input variables on left pane, and you can see results on right pane:

* Expected value for miles per gallon
* Plot that demonstrates predicted value vs training data.

We do prediction with standard function predict.lm

```{r eval=FALSE}
mpg<-predict.lm(fit3, newdata=data.frame(wt,qsec,am))
```

---
## Results

You can see data with plot and text output.

```{r echo=FALSE}

library(ggplot2)
fit3 <- lm(mpg ~ wt + am + qsec, data=mtcars)  
multiplot <- function(..., plotlist=NULL, cols) {
  require(grid)
  
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  
  numPlots = length(plots)
  
  # Make the panel
  plotCols = cols                          # Number of columns of plots
  plotRows = ceiling(numPlots/plotCols) # Number of rows needed, calculated from # of cols
  
  # Set up the page
  grid.newpage()
  pushViewport(viewport(layout = grid.layout(plotRows, plotCols)))
  vplayout <- function(x, y)
    viewport(layout.pos.row = x, layout.pos.col = y)
  
  # Make each plot, in the correct location
  for (i in 1:numPlots) {
    curRow = ceiling(i/plotCols)
    curCol = (i-1) %% plotCols + 1
    print(plots[[i]], vp = vplayout(curRow, curCol ))
  }
  
}           

wt<-2.70
qsec<-18
am<-1


mpg<-predict.lm(fit3, newdata=data.frame(wt,qsec,am))

mpg
           
           g1<-ggplot(mtcars, aes(x=wt, y=mpg, colour=am)) + geom_point() + ggtitle("MPG vs Weight")+annotate("point",size = 5, shape = 19, color = "#00FF00", x = wt, y = mpg)
           g2<-ggplot(mtcars, aes(x=qsec, y=mpg, colour=am)) + geom_point() +ggtitle("MPG vs Qsec")+annotate("point",size = 5, shape = 19, color = "#00FF00", x = qsec, y = mpg)
           multiplot(g1, g2, cols = 2)
```



